---
execute: 
  eval: false
---

# Global Setup

This section documents the global environment and configuration loaded at app startup, primarily from `global.R` and supporting files in the `Standards/` directory.

## Package Loading

All required packages are loaded at the beginning of `global.R`, grouped by purpose: Shiny components, plotting, data manipulation, reading data, and mapping.

## Standards and Constants

The file `Standards/app_standards.R` is sourced first and defines:

-   `current_years`: named list for year references, including min/max years and grouped periods

-   `constants`: general constants like the name for California (`"CALIFORNIA"`) and version info

-   `links()`: a function that loads lookup tables from Excel and CSV files for race, age, cause of death, counties, education, etc.

-   `choices()`: returns formatted lists for dropdowns — LHJs, causes, and death measures

-   `appText()`: loads display strings (e.g. tooltips, disclaimers) from Word documents using `docxtractr`

-   `plot_colors()`: defines custom color palettes for race, age, gender, and cause types

-   `ggplot_standards()`: sets up ggplot2 theming, line widths, point shapes, and text sizes

These are returned as structured lists: `choices`, `links`, `appText`, `plot_colors`, and `ggplot_standards`, all available globally.

## Lazy Data Loader

A custom function `lazy_load()` is defined to load files **once per session**, storing the result in a `cache` environment. It supports:

-   `.rds`, `.csv`, `.xlsx`, `.rdata`, `.shp`, and `.docx` files

-   Optional sheet selection or table extraction

-   `clear_cache()` helper to wipe the environment when needed

## Inputs and Modules

Global input functions and widgets are sourced from:

```{r}
source("myFunctions/inputs/input_widgets.R")
source("myFunctions/inputs/input_functions.R")
```

All plotting functions are sourced from `myFunctions/` including maps, ranks, trends, disparities, life expectancy, and demographics.

Modules are loaded by sourcing all `.R` files in the `myFunctions/modules/` folder:

```{r}
lapply(list.files("myFunctions/modules/", pattern = "\\.R$", full.names = TRUE), source)
```

This architecture ensures that all helper functions, shared resources, and modules are available before the UI and server launch.
